---
title: "HCDR02"
author: "Gabrielle Saga"
date: "13/11/2021"
output: html_document
---

# 1. Data Importation
```{r import libraries}
packages <- c("caTools", "dplyr", "ggplot2", "rpart", "caret", "randomForest", "ipred", "MASS", "survival", "neuralnet", "adabag", "xgboost", "e1071", "class", "rpart.plot", "vip", "pdp", "glmnet", "tidyverse", "fastDummies", "correlation", "corrplot", "data.table", "psych", "skimr", "reshape2", "tidyr", "dataPreparation")
lapply(packages, require, character.only=TRUE)
getwd()
```

```{r import data}
df_train <- read.csv("application_train.csv")
df_bureau <- read.csv("bureau.csv")

# head of datasets imported
head(df_train)
head(df_bureau)

# bureau
summary(df_bureau)
nrow(df_bureau)

#train
summary(df_train)
nrow(df_train)
#any(is.na(df_train))
#any(duplicated(df_train))
# drop sk_id_curr
#df <- df_train[, -c(1)]
#head(df)
# missing values
#table(is.na(df))
#nrow(df)
```

# 2. Data Manipulation
```{r}
df_bureau[ which(df_bureau$CREDIT_ACTIVE == "Bad debt"), ]

# means
bureau_means <- df_bureau %>% group_by(SK_ID_CURR) %>% summarize_if(is.numeric, mean)
summary(bureau_means)
nrow(bureau_means)

# sums
bureau_sums <- df_bureau %>% group_by(SK_ID_CURR) %>% summarize_if(is.numeric, sum)
summary(bureau_sums)
nrow(bureau_sums)

# count
bureau_count <- df_bureau %>% group_by(CREDIT_ACTIVE, SK_ID_CURR) %>% summarize(counts=n()) %>% spread(CREDIT_ACTIVE, counts)
bureau_count <- bureau_count %>% group_by(SK_ID_CURR) %>% summarize_all(sum, na.rm=TRUE)
summary(bureau_count)
nrow(bureau_count)

# all
bureau_all <- merge(merge(bureau_means, bureau_sums, by="SK_ID_CURR"), bureau_count, by="SK_ID_CURR")
summary(bureau_all)
bureau_all[is.na(bureau_all)] <- 0
```

```{r}
df_train[ , grepl("FLAG", names(df_train))] <- lapply(df_train[, grepl("FLAG", names(df_train))], factor)
df_train[ , grepl("FLAG", names(df_train))]
df_train[ , 'TARGET'] <- as.factor(df_train[, 'TARGET'])
nrow(df_train)
summary(df_train)
```

```{r}
df_train <- dplyr::left_join(df_train, bureau_all, by="SK_ID_CURR")
head(df_train)
summary(df_train)
```

```{r remove unnecessary columns}
drop <- c("SK_ID_CURR",
          "FLAG_CONT_MOBILE",
          "FLAG_DOCUMENT_10",
          "FLAG_DOCUMENT_11",
          "FLAG_DOCUMENT_12",
          "FLAG_DOCUMENT_13",
          "FLAG_DOCUMENT_14",
          "FLAG_DOCUMENT_15",
          "FLAG_DOCUMENT_16",
          "FLAG_DOCUMENT_17",
          "FLAG_DOCUMENT_18",
          "FLAG_DOCUMENT_19",
          "FLAG_DOCUMENT_2",
          "FLAG_DOCUMENT_20",
          "FLAG_DOCUMENT_21",
          "FLAG_DOCUMENT_4",
          "FLAG_DOCUMENT_5",
          "FLAG_DOCUMENT_7",
          "FLAG_DOCUMENT_9",
          "FLAG_MOBIL",
          "BASEMENTAREA_AVG",
          "BASEMENTAREA_MEDI",
          "BASEMENTAREA_MODE",
          "COMMONAREA_AVG",
          "COMMONAREA_MEDI",
          "COMMONAREA_MODE",
          "ELEVATORS_AVG",
          "ELEVATORS_MEDI",
          "ELEVATORS_MODE",
          "EXT_SOURCE_1",
          "FLOORSMIN_AVG",
          "FLOORSMIN_MEDI",
          "FLOORSMIN_MODE",
          "LANDAREA_AVG",
          "LANDAREA_MODE",
          "LIVINGAPARTMENTS_AVG",
          "LIVINGAPARTMENTS_MEDI",
          "LIVINGAPARTMENTS_MODE",
          "NONLIVINGAPARTMENTS_AVG",
          "NONLIVINGAPARTMENTS_MEDI",
          "NONLIVINGAPARTMENTS_MODE",
          "NONLIVINGAREA_AVG",
          "NONLIVINGAREA_MODE",
          "OWN_CAR_AGE",
          "YEARS_BUILD_AVG",
          "YEARS_BUILD_MEDI",
          "YEARS_BUILD_MODE",
          "APARTMENTS_AVG",
          "YEARS_BEGINEXPLUATATION_AVG", 
          "ENTRANCES_AVG", 
          "FLOORSMAX_AVG", 
          "LIVINGAREA_AVG",
          "APARTMENTS_MODE", 
          "YEARS_BEGINEXPLUATATION_MODE",
          "ENTRANCES_MODE", 
          "LIVINGAREA_MODE",
          "APARTMENTS_MEDI",
          "YEARS_BEGINEXPLUATATION_MEDI", 
          "ENTRANCES_MEDI",              
          "FLOORSMAX_MEDI",              
          "LANDAREA_MEDI",               
          "LIVINGAREA_MEDI",             
          "NONLIVINGAREA_MEDI",          
          "TOTALAREA_MODE",
          "FLOORSMAX_MODE",
          "EXT_SOURCE_3",
          "SK_ID_BUREAU",
          "SK_ID_BUREAU.x",
          "SK_ID_BUREAU.y")
df = df_train[,!(names(df_train) %in% drop)]
head(df)
```

```{r fill and drop null values}
HasNullFactor <- c("CNT_FAM_MEMBERS", 
                   "DEF_30_CNT_SOCIAL_CIRCLE", 
                   "DEF_60_CNT_SOCIAL_CIRCLE", 
                   "AMT_REQ_CREDIT_BUREAU_HOUR", 
                   "AMT_REQ_CREDIT_BUREAU_DAY", 
                   "AMT_REQ_CREDIT_BUREAU_MON", 
                   "AMT_REQ_CREDIT_BUREAU_QRT", 
                   "AMT_REQ_CREDIT_BUREAU_YEAR")

df_reqCredit <- df %>% group_by(TARGET) %>% summarise(across(HasNullFactor, mean, na.rm=TRUE))
head(df_reqCredit)

for (columnName in HasNullFactor){
  df[[columnName]][is.na(df[columnName])] <- round(mean(as.numeric(df[[columnName]]), na.rm = TRUE))
}

HasNullNumeric <- c("EXT_SOURCE_2", "AMT_GOODS_PRICE", "AMT_ANNUITY")

for (columnName in HasNullNumeric){
  df[columnName][is.na(df[columnName])] <- colMeans(df[columnName], na.rm = TRUE)
}

df <- na.omit(df)
head(df)
```

```{r}
table(df$TARGET)
```

```{r}
df <- df %>% mutate(CODE_GENDER = na_if(CODE_GENDER, "XNA"),
                    ORGANIZATION_TYPE = na_if(ORGANIZATION_TYPE, "XNA"))
df <- na.omit(df)
table(df$TARGET)
```

```{r outliers}
NumericColumns <- c("AMT_INCOME_TOTAL", 
                    "AMT_CREDIT", 
                    "AMT_ANNUITY", 
                    "AMT_GOODS_PRICE",
                    "REGION_POPULATION_RELATIVE", 
                    "DAYS_BIRTH", 
                    "DAYS_EMPLOYED", 
                    "DAYS_REGISTRATION", 
                    "DAYS_ID_PUBLISH", 
                    "EXT_SOURCE_2", 
                    "OBS_30_CNT_SOCIAL_CIRCLE", 
                    "OBS_60_CNT_SOCIAL_CIRCLE", 
                    "DAYS_LAST_PHONE_CHANGE")
#Histogram with Normal Curve
for (columnName in NumericColumns){
  print(columnName)
  x<- df[[columnName]]
  print(summary(x))
    h<-hist(x, breaks=10, col="red", xlab=columnName, main="Histogram with Normal Curve")
  xfit<-seq(min(x),max(x),length=40)
  yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
  yfit <- yfit*diff(h$mids[1:2])*length(x)
  lines(xfit, yfit, col="blue", lwd=2)
}
#Remove Outliers 4STD
df <- remove_sd_outlier(df, cols = NumericColumns, n_sigmas = 4, verbose = TRUE)

for (c in colnames(df)){
       if(class(df[[c]])=='numeric' | class(df[[c]])=='integer'  ) {
           df_uniq = unique(df[[c]])
           print(c,str(length(df_uniq)))
           if(length(df_uniq) <= 30){
             df[[c]] = as.factor(df[[c]])
           }
    }
}
```

```{r}
skimr::skim(df)
```

```{r outliers boxplots}
for (c in colnames(df)){
       if(class(df[[c]])=='numeric' | class(df[[c]])=='integer'  ) {
        boxplot(df[[c]] ~ TARGET, data = df, col = "red",ylab = c)   
    }
}
```

```{r outliers histograms}
for (c in colnames(df)){
  if(class(df[[c]])=='numeric' | class(df[[c]])=='integer'  ) {
    df_uniq = unique(df[[c]])
      print(c)
      binw = (max(df[[c]], na.rm=T) - min(df[[c]], na.rm=T)) / sqrt(307512)
      print(binw)
        (ggplot(df, aes(x=df[[c]], fill=TARGET)) +
        geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity') +
            scale_fill_manual(values=c("#69b3a2", "#404080")) +
            theme_bw() +
            xlab(c)+
            labs(fill=""))  %>% print()
  }
}
```

```{r}
head(df)
```

```{r}
table(df$`Bad debt`)
```

```{r separating categorical and continuous}
# categorical
catdf <- subset(df, select=c(NAME_CONTRACT_TYPE, 
                             CODE_GENDER, 
                             FLAG_OWN_CAR, 
                             FLAG_OWN_REALTY, 
                             NAME_TYPE_SUITE, 
                             NAME_INCOME_TYPE, 
                             NAME_EDUCATION_TYPE, 
                             NAME_FAMILY_STATUS, 
                             NAME_HOUSING_TYPE, 
                             OCCUPATION_TYPE, 
                             WEEKDAY_APPR_PROCESS_START, 
                             ORGANIZATION_TYPE, 
                             FONDKAPREMONT_MODE, 
                             HOUSETYPE_MODE, 
                             WALLSMATERIAL_MODE, 
                             EMERGENCYSTATE_MODE))
head(catdf)

# continuous
condf <- subset(df, select=c(TARGET,
                             FLAG_EMP_PHONE,
                             FLAG_WORK_PHONE,
                             FLAG_PHONE,
                             FLAG_EMAIL,
                             FLAG_DOCUMENT_3,
                             FLAG_DOCUMENT_6,
                             FLAG_DOCUMENT_8,
                             CNT_CHILDREN, 
                             AMT_INCOME_TOTAL, 
                             AMT_CREDIT, 
                             AMT_ANNUITY, 
                             AMT_GOODS_PRICE, 
                             REGION_POPULATION_RELATIVE, 
                             DAYS_BIRTH, 
                             DAYS_EMPLOYED, 
                             DAYS_REGISTRATION, 
                             DAYS_ID_PUBLISH, 
                             CNT_FAM_MEMBERS, 
                             REGION_RATING_CLIENT, 
                             REGION_RATING_CLIENT_W_CITY, 
                             HOUR_APPR_PROCESS_START, 
                             REG_REGION_NOT_LIVE_REGION, 
                             REG_REGION_NOT_WORK_REGION, 
                             LIVE_REGION_NOT_WORK_REGION, 
                             REG_CITY_NOT_LIVE_CITY, 
                             REG_CITY_NOT_WORK_CITY, 
                             LIVE_CITY_NOT_WORK_CITY, 
                             EXT_SOURCE_2, 
                             OBS_30_CNT_SOCIAL_CIRCLE, 
                             DEF_30_CNT_SOCIAL_CIRCLE, 
                             OBS_60_CNT_SOCIAL_CIRCLE, 
                             DEF_60_CNT_SOCIAL_CIRCLE, 
                             DAYS_LAST_PHONE_CHANGE, 
                             AMT_REQ_CREDIT_BUREAU_HOUR, 
                             AMT_REQ_CREDIT_BUREAU_DAY, 
                             AMT_REQ_CREDIT_BUREAU_WEEK, 
                             AMT_REQ_CREDIT_BUREAU_MON, 
                             AMT_REQ_CREDIT_BUREAU_QRT, 
                             AMT_REQ_CREDIT_BUREAU_YEAR,
                             DAYS_CREDIT.x,
                             CREDIT_DAY_OVERDUE.x,
                             DAYS_CREDIT_ENDDATE.x,
                             DAYS_ENDDATE_FACT.x,
                             AMT_CREDIT_MAX_OVERDUE.x,
                             CNT_CREDIT_PROLONG.x,
                             AMT_CREDIT_SUM.x,
                             AMT_CREDIT_SUM_DEBT.x,
                             AMT_CREDIT_SUM_LIMIT.x,
                             AMT_CREDIT_SUM_OVERDUE.x,
                             DAYS_CREDIT_UPDATE.x,
                             AMT_ANNUITY.x,
                             DAYS_CREDIT.y,
                             CREDIT_DAY_OVERDUE.y,
                             DAYS_ENDDATE_FACT.y,
                             AMT_CREDIT_MAX_OVERDUE.y,
                             CNT_CREDIT_PROLONG.y,
                             AMT_CREDIT_SUM.y,
                             AMT_CREDIT_SUM_DEBT.y,
                             AMT_CREDIT_SUM_LIMIT.y,
                             AMT_CREDIT_SUM_OVERDUE.y,
                             DAYS_CREDIT_UPDATE.y,
                             AMT_ANNUITY.y,
                             Active,
                             Closed,
                             Sold,
                             `Bad debt`))
head(condf)
```

```{r renaming columns}
#categorical
catdf <- catdf %>% rename(ContractType=NAME_CONTRACT_TYPE,
                          Gender=CODE_GENDER,
                          OwnCar=FLAG_OWN_CAR,
                          OwnRealty=FLAG_OWN_REALTY,
                          Suite=NAME_TYPE_SUITE,
                          IncomeType=NAME_INCOME_TYPE,
                          Education=NAME_EDUCATION_TYPE,
                          FamStat=NAME_FAMILY_STATUS,
                          Housing=NAME_HOUSING_TYPE,
                          Occ=OCCUPATION_TYPE,
                          ProcessStart=WEEKDAY_APPR_PROCESS_START,
                          Org=ORGANIZATION_TYPE,
                          Account=FONDKAPREMONT_MODE,
                          HouseMode=HOUSETYPE_MODE,
                          Material=WALLSMATERIAL_MODE,
                          Emergency=EMERGENCYSTATE_MODE)

#continuous
condf <- condf %>% rename(EmpPhone_Yes=FLAG_EMP_PHONE,
                          WorkPhone_Yes=FLAG_WORK_PHONE,
                          Phone_Yes=FLAG_PHONE,
                          Email_Yes=FLAG_EMAIL,
                          Doc3_Yes=FLAG_DOCUMENT_3,
                          Doc6_Yes=FLAG_DOCUMENT_6,
                          Doc8_Yes=FLAG_DOCUMENT_8,
                          Children=CNT_CHILDREN, 
                          Income=AMT_INCOME_TOTAL, 
                          Credit=AMT_CREDIT, 
                          Annuity=AMT_ANNUITY, 
                          GoodsPrice=AMT_GOODS_PRICE, 
                          Population=REGION_POPULATION_RELATIVE,
                          BirthDays=DAYS_BIRTH, 
                          EmployedDays=DAYS_EMPLOYED, 
                          RegistrationDays=DAYS_REGISTRATION, 
                          IdPubDays=DAYS_ID_PUBLISH, 
                          FamMembers=CNT_FAM_MEMBERS, 
                          RRC=REGION_RATING_CLIENT, 
                          RRCC=REGION_RATING_CLIENT_W_CITY, 
                          StartHourProcess=HOUR_APPR_PROCESS_START, 
                          RRNLR=REG_REGION_NOT_LIVE_REGION, 
                          RRNWR=REG_REGION_NOT_WORK_REGION, 
                          LRNWR=LIVE_REGION_NOT_WORK_REGION, 
                          RCNLC=REG_CITY_NOT_LIVE_CITY, 
                          RCNWC=REG_CITY_NOT_WORK_CITY, 
                          LCNWC=LIVE_CITY_NOT_WORK_CITY, 
                          ExtSource2=EXT_SOURCE_2, 
                          Social30oc=OBS_30_CNT_SOCIAL_CIRCLE, 
                          Social30dc=DEF_30_CNT_SOCIAL_CIRCLE, 
                          Social60oc=OBS_60_CNT_SOCIAL_CIRCLE, 
                          Social60dc=DEF_60_CNT_SOCIAL_CIRCLE, 
                          SLPC=DAYS_LAST_PHONE_CHANGE, 
                          CBHour=AMT_REQ_CREDIT_BUREAU_HOUR, 
                          CBDay=AMT_REQ_CREDIT_BUREAU_DAY, 
                          CBWeek=AMT_REQ_CREDIT_BUREAU_WEEK, 
                          CBMonth=AMT_REQ_CREDIT_BUREAU_MON, 
                          CBQrt=AMT_REQ_CREDIT_BUREAU_QRT, 
                          CBYear=AMT_REQ_CREDIT_BUREAU_YEAR,
                          CrDays.x=DAYS_CREDIT.x,
                          CrOverdue.x=CREDIT_DAY_OVERDUE.x,
                          CrEnddate.x=DAYS_CREDIT_ENDDATE.x,
                          FactEnddate.x=DAYS_ENDDATE_FACT.x,
                          MaxOverdue.x=AMT_CREDIT_MAX_OVERDUE.x,
                          Prolong.x=CNT_CREDIT_PROLONG.x,
                          Sum.x=AMT_CREDIT_SUM.x,
                          SumDebt.x=AMT_CREDIT_SUM_DEBT.x,
                          SumLimit.x=AMT_CREDIT_SUM_LIMIT.x,
                          SumOverdue.x=AMT_CREDIT_SUM_OVERDUE.x,
                          Update.x=DAYS_CREDIT_UPDATE.x,
                          Annuity.x=AMT_ANNUITY.x,
                          Days.y=DAYS_CREDIT.y,
                          Overdue.y=CREDIT_DAY_OVERDUE.y,
                          FactEnddate.y=DAYS_ENDDATE_FACT.y,
                          MaxOverdue.y=AMT_CREDIT_MAX_OVERDUE.y,
                          Prolong.y=CNT_CREDIT_PROLONG.y,
                          Sum.y=AMT_CREDIT_SUM.y,
                          SumDebt.y=AMT_CREDIT_SUM_DEBT.y,
                          SumLimit.y=AMT_CREDIT_SUM_LIMIT.y,
                          SumOverdue.y=AMT_CREDIT_SUM_OVERDUE.y,
                          Update.y=DAYS_CREDIT_UPDATE.y,
                          Annuity.y=AMT_ANNUITY.y,
                          BadDebt=`Bad debt`)
```

```{r dummy variables}
library('fastDummies')
catdf2 <- fastDummies::dummy_cols(catdf, remove_first_dummy = TRUE)
catdf2 <- catdf2[, -c(1:16)]
#catdf3 <- cbind(catdf2, df[c("TARGET", 
#                             "FLAG_EMP_PHONE", 
#                             "FLAG_WORK_PHONE", 
#                             "FLAG_PHONE", 
#                             "FLAG_EMAIL", 
#                             "FLAG_DOCUMENT_3", 
#                             "FLAG_DOCUMENT_6", 
#                             "FLAG_DOCUMENT_8",
#                             "Bad debt")])
#catdf3 <- catdf3 %>% rename(EmpPhone_Yes=FLAG_EMP_PHONE,
#                            WorkPhone_Yes=FLAG_WORK_PHONE,
#                            Phone_Yes=FLAG_PHONE,
#                            Email_Yes=FLAG_EMAIL,
#                            Doc3_Yes=FLAG_DOCUMENT_3,
#                            Doc6_Yes=FLAG_DOCUMENT_6,
#                            Doc8_Yes=FLAG_DOCUMENT_8,
#                            BadDebt=`Bad debt`)
head(catdf2)
#head(catdf3)
```

```{r final dataset}
df2 <- cbind(condf, catdf2)
df2 <- df2 %>% relocate(TARGET)
head(df2)
```

# 3. Logistic Regression
```{r train and test}
library(caTools)
library(caret)

df2$TARGET <- factor(df2$TARGET, levels = c(0,1))

options(scipen=999)
set.seed(100)
index <- createDataPartition(df2$TARGET, p=.7, list=FALSE)

dfTrain <- df2[index, ]
dfTest <- df2[-index, ]

logreg <- glm(TARGET ~., family=binomial(link = "logit"), data=dfTrain)
summary(logreg)
```

Statistically significant values are: Children, Income, Credit, Annuity, GoodsPrice, Population, BirthDays, EmployedDays, IdPubDays, FamMembers, RRCC (Region Rating Client w/ City), ExtSource2, LivingApts, CBYear, Gender_M, OwnCar_Y, OwnRealty_Y, Married, Separated, Single, Accountants, Drivers, Laborers, Low-Skill Laborers, Material_Others, WorkPhone_Yes, Doc3_Yes, doc6_Yes, Doc8_Yes

```{r anova}
anova(logreg, test="Chisq")
```

```{r Classification Table - Train}
pred_prob <- predict(logreg, dfTest, type="response")

#train
dfTrain$pred_target <- ifelse(logreg$fitted.values>=.5, "YES", "NO")
ctabTrain <- table(dfTrain$TARGET, dfTrain$pred_target)
print(ctabTrain)

#test
dfTest$pred_target <- ifelse(pred_prob>=.5, "YES", "NO")
ctabTest <- table(dfTest$TARGET, dfTest$pred_target)
print(ctabTest)
```

```{r accuracy}
#train
accuracyTrain <- sum(diag(ctabTrain))/sum(ctabTrain)*100
print(accuracyTrain)

#test
accuracyTest <- sum(diag(ctabTest))/sum(ctabTest)*100
print(accuracyTest)
```

92.89% of all the observations are correctly classified in the training dataset. Overall correct classification of the test dataset is 92.78%. The test dataset maybe a little bit lower than the train dataset. It is still overall about 92% which is still a good indicator of its 

```{r misclassification rate}
# true positive rate
tpr <- (ctabTrain[2,2]/sum(ctabTrain[2, ]))*100
# true negative rate
tnr <- (ctabTrain[1,1]/sum(ctabTrain[1, ]))*100
# precision
precision <- (ctabTrain[2,2]/sum(ctabTrain[,2]))*100
# f-score
fScore <- (2*precision*tpr/(precision+tpr))/100

print(tpr)
print(tnr)
print(precision)
print(fScore)
```

The true positive rate of our model is 0.11% while our true negative rate is 99.99%. Precision of how often predicted true values are actually true is 47.92%. The model has a 0.00% f-score which means that the model does not represent perfect precision and recall. 

```{r ROC curve}
library(pROC)
roc <- roc(dfTrain$TARGET, logreg$fitted.values)
auc(roc)
```

However the area under the curve which is 0.71 is somewhat a good model. 

```{r concordance}
library(InformationValue)
Concordance(logreg$y, logreg$fitted.values)
```


